Quantitative processing of broadband data as implemented in a scientific split-beam echosounder

### 2023-09-29 Paper/Manuscript.tex
Error fixes

\title[]{Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder}

\begin{abstract}
1. The use of quantitative broadband echosounders for biological studies and surveys can offer considerable advantages over narrowband echosounders. These include improved spectral-based target identification and significantly increased ability to resolve individual targets. An understanding of current processing steps is required to fully utilize and further develop broadband acoustic methods in marine ecology.\linebreak 
2. We describe the steps involved in processing broadband acoustic data from raw data to frequency dependent target strength (TS(f)) and volume backscattering strength (Sv(f)) using data from the EK80 broadband scientific echosounder as examples. Although the overall processing steps are described and build on established methods from the literature, multiple choices need to be made during implementation. \linebreak
3. To highlight and discuss some of these choices and facilitate a common understanding within the community, we have also developed a Python code which will be made publicly available and open source. The code follows the steps using raw data from two single pings, showing the step-by-step processing from raw data to TS(f) and Sv(f). \linebreak
4. This code can serve as a reference for developing custom code or implementation in existing processing pipelines, as an educational tool and as a starting point for further development of broadband acoustic methods in fisheries acoustics.\linebreak

@@

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the ensonified volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_c 
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\freqsym) \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the electric power received in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, $\tslide$ the duration of the time window, excluding the zero-padded portion if applied, used to evaluate the frequency spectrum, $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and $\eqang(\freqsym)$ is the two-way equivalent beam angle. The two-way equivalent beam angle is a function of frequency that is derived from an empirical estimate of $\eqang$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram_m_n}
\caption{\label{fi:Fig_Sv_echogram} Illustration of the volume backscattering strength as a function of frequency, Sv(f). The fish school is seen as a registration between 15 and 35 m range, and the sea floor is seen at approximately 50 m. (a) Sv as a function of ping number and range range for the raw data file used in the Sv(f) example. The red vertical line indicates the ping that is used to illustrate the Sv(f) processing used in (b). (b) Sv(f) as a function of frequency and range for a single ping indicated in (a) with a vertical red line. In this example, the decimated sampling rate ($\fsdec$, \autoref{eq:fsdec}) is 93.75 kHz, the nominal pulse duration ($\tnom$) is 2 ms, and the effective pulse duration ($\teff$, \autoref{eq:TauEff}) is 0.02 ms.}
\end{figure}

>>>>

\title[]{Quantitative processing of broadband data as implemented in a scientific split-beam echosounder}

\begin{abstract}
1. The use of quantitative broadband echosounders for biological studies and surveys can offer considerable advantages over narrowband echosounders. These include improved spectral-based target identification and significantly increased ability to resolve individual targets. An understanding of current processing steps is required to fully utilize and further develop broadband acoustic methods in marine ecology.\linebreak 
2. We describe the steps involved in processing broadband acoustic data from raw data to frequency dependent target strength ($\ts(\freqsym)$) and volume backscattering strength ($\sv(\freqsym)$) using data from the EK80 broadband scientific echosounder as examples. Although the overall processing steps are described and build on established methods from the literature, multiple choices need to be made during implementation. \linebreak
3. To highlight and discuss some of these choices and facilitate a common understanding within the community, we have also developed a Python code which will be made publicly available and open source. The code follows the steps using raw data from two single pings, showing the step-by-step processing from raw data to $\ts(\freqsym)$ and $\sv(\freqsym)$. \linebreak
4. This code can serve as a reference for developing custom code or implementation in existing processing pipelines, as an educational tool and as a starting point for further development of broadband acoustic methods in fisheries acoustics.\linebreak

@@

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the ensonified volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_c 
- 10\log_{10}\left( \frac{\ptxe \wlen^2(\freqsym) \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the electric power received in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and $\eqang(\freqsym)$ is the two-way equivalent beam angle. $\tslide$ is the duration of the time window, excluding the zero-padded portion if applied, used to evaluate the frequency spectrum. Note that for the single frequency, narrowband, case the pulse duration is used, for the broadband case $\tslide$ is used. The two-way equivalent beam angle is a function of frequency that is derived from an empirical estimate of $\eqang$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram_m_n}
\caption{\label{fi:Fig_Sv_echogram} Illustration of the volume backscattering strength as a function of frequency, Sv(f). The fish school is seen as a registration between 15 and 35 m range, and the sea floor is seen at approximately 50 m. (a) Pulse compressed Sv as a function of ping number and range for the raw data file used in the Sv(f) example. The red vertical line indicates the ping that is used to illustrate the Sv(f) processing. (b) Sv as a function of frequency and range for the single ping indicated in (a) with a vertical red line. In this example, the decimated sampling rate ($\fsdec$, \autoref{eq:fsdec}) is 93.75 kHz, the nominal pulse duration ($\tnom$) is 2 ms, and the effective pulse duration ($\teff$, \autoref{eq:TauEff}) is 0.02 ms.}
\end{figure}
